Partitioned Local Depth (PaLD) Community Analyses in R

### 2023-05-02 r-journal/dagostino-mcgowan.tex
add sentence

We present a new package, \CRANpkg{pald}, for calculating Partitioned
Local Depth (PaLD) probabilities, implementing community analyses, and
creating data visualizations to display community structure. This paper
will describe how to use the package, walk through several examples, and
compare the method to commonly used clustering algorithms.

@@

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH aa6899c UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from aa6899c (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from 7ab7e40:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}

>>>>

We present a new package, \CRANpkg{pald}, for calculating Partitioned
Local Depth (PaLD) probabilities, implementing community analyses, and
creating data visualizations to display community structure. This paper
will describe how to use the package, walk through several examples, and
compare the method to commonly used techniques in R. Together, these
demonstrate both the novelty of the method and utility of the
implementation in package described.

@@

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH f9306e2 UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from f9306e2 (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from 2660ad9:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}
